Generation of TypeScript Declaration Files from JavaScript Code

### 2021-05-26 mplr-2021/main.tex
discussion of dts-gen

Unlike \texttt{dts-gen}, a TypeScript package that generates a template for a declaration
file which only analyzes the structure of the module, we determine the kind of declaration file by examining the usage
of the module. If the
imported entity is used solely as a function as in Figure~\ref{fig:example-module-function}, the
generated declaration file follows the \textbf{module-function} template as shown in Figure~\ref{fig:template-module-function}.
If the example only accesses properties of the imported entity as in
Figure~\ref{fig:example-module}, we generate according to the \textbf{module} template (Figure~\ref{fig:template-module}).
If the imported entity is used with \lstinline/new/ to create new instances as in
Figure~\ref{fig:example-class}, we generate a \textbf{module-class} template (Figure~\ref{fig:template-class}).
While it is possible to create a library of undetermined category, our selection is driven
by the examples in the documentation and 
hence reflects the developers intent.
% Run-time analysis proves useful in this case,
% since it is not sufficient to statically analyze the exported module.

>>>>

The Typescript project provides a package \texttt{dts-gen}, which
generates a template for a declaration file by analyzing the structure
of the module. The resulting file is intended as a starting point for further
manual development of the declaration file. 
Unlike \texttt{dts-gen} we determine the kind of declaration file by
examining the \emph{usage} of the module. If the imported entity is
used solely as a function as in
Figure~\ref{fig:example-module-function}, the 
generated declaration file follows the \textbf{module-function}
template as shown in Figure~\ref{fig:template-module-function}. 
If the example only accesses properties of the imported entity as in
Figure~\ref{fig:example-module}, we generate the declarations
according to the \textbf{module} template
(Figure~\ref{fig:template-module}). 
If the imported entity is used with \lstinline/new/ to create new instances as in
Figure~\ref{fig:example-class}, we generate a \textbf{module-class} template (Figure~\ref{fig:template-class}).
While it is possible to create a library of undetermined category, our selection is driven
by the examples in the documentation and 
hence reflects the developer's intent.
% Run-time analysis proves useful in this case,
% since it is not sufficient to statically analyze the exported module.
